---
title: "linear model from Web"
author: "Aeilani Felix "
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Introduction 

We predict a stimulated strength scored based from the Arm and Grip strength.

Arm is a Numerical variable

Grip is Numerical as well 

So we use the Numerical-Num Helper file

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
lmr = lm(SIMS~ARM, data = data )
abline(lmr)
```

According to the scatter plot , it appears to be that this is a strong positive linear correlation between the two numerical variables.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.68. This means that ARM is related to SIMS score

### Inferential  (Build model.1)

```{r}
summary(lmr)
newdata = c(GRIP = 94, ARM = 88 )
```

This shows that the p-value is 0.00000000000000022. This number is far lower than 0.5

#### Predict at target point

```{r}
predictSIM = predict.lm(lmr, newdata = data.frame (GRIP = 94, ARM = 88))
print(predictSIM)
```

Based of this code , the SIMS~ARM target point is 0.706.

#### scatterplot with model fit

```{r}
plot(lmr)
```

These model fits show that my scatter plots are accurate because they all relatively have a straight line. Of course, not perfectly, but this is as accurate as I can get with the model fit. The bottom it shows lm(SIMS~ARM) so I am 100% sure that I'm showing the correct numerical variables for this model. 
  
## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

