---
title: "linear model from Web"
author: 'Aeilani Felix '
date: "Spring 2024"
output:
  pdf_document:
    toc: true
    toc_depth: '5'
  html_document:
    toc: true
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction
We will produce three equation models to get 
1. sim score based on arm strength 
2. sim score based on grip strength
3. sim score based on arm and grip strength 
 
 For each model we will predict sims for arm=88, grip=94

#Method 
We have numerical response (sims score) and numerical explanatory variables (arm and grip strength)

So we use the Numerical-Num Helper file

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

According to the scatter plot , it appears to be that this is a strong positive linear correlation between the two numerical variables.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.68. This means that ARM is related to SIMS score

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

This shows that the p-value is 0.0000000000000002. This number is far lower than 0.5

#### Predict at target point
```{r}
SIMSpredict = predict(model.1, newdata = data.frame( GRIP = 94, ARM = 88),interval = "confidence")
print(predictSIM)
```

Based of this code , the SIMS~ARM target point is 0.71

#### scatterplot with model fit
```{r}
plot(ARM~SIMS, data=data)
abline(model.1, color="blue")
```

This model fit show that SIMS increases and the ARM increases, so this is a positive relationship. 

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
abline(model.1,col="red")
```

According to this graph is shows that we have a positive linear relation.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The numerical value is 0.64.

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The minimum value is -2.9295. The Q1 value is -0.8708. The Q3 value is .8039. The median is -0.1219. The max is 3.3494.The p-value is 0.00000000000000022.

#### predict model.2 at target point
```{r}
mydata <-data.frame(GRIP = 94, ARM = 88)
predict.lm(model.2, mydata, interval = "prediction")
```

#### now add the model fit to our plot for model.2
```{r}
plot(SIMS~GRIP, data=data)
abline(model.2,col="green")
```

This graph shows us that this is a positive correlation.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
m = data.frame(data['GRIP'], data['ARM'], data['SIMS'])
cor(m)
```

The table shows that SIMS correlates with GRIP in a positive manner (0.64) and SIMS correlates with ARM also in a positive manner (0.69). This says that these variable are useful in predictions SIMS.
  
```{r}
plot(data$GRIP, data$ARM)
```

Plot shows that the GRIP and ARM are not independent, so this is not necessarily a good model.

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 = lm(SIMS~GRIP+ ARM, data=data)
print(summary.lm(model.3))
new
``` 
#### predict model.3 at target point

```{r}
newPoint=data.frame(GRIP=94, ARM=88)
predict.lm(model.3, newPoint, interval ='prediction' )
```

The 95% confidence interval is SIMS is between -2.13 and 2.43. Since this interval contains 0, we do not have a very good prediction for SIMS.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```
p-value is 0.00000499, this is less than 0.05 so we conclude that model.3 is better/worse than model.1

### Model.2 vs Model.3

```{r}
anova(model.2, model.3)
```

p-value is 0.000000001495. 

## Informally compare Model.1 with model.2

In conclusion, model 3 is the best because it has a smaller RSS than both model 1 and model 2. Model 1 is better than model 2., but in order for it to be better, it would need a smaller RSS. In the end, we are rejecting the null hypothesis and model 3 is the best overall. 